% !TeX root = ../example.tex

% 中英文摘要和关键字

\begin{abstract}
  摘要是一篇具有独立性和完整性的短文，应概况而扼要地反映出论文的主要内容。
  摘要应对论文所研究的问题及其研究目的进行描述，对研究方法和过程进行简单介绍，对研究成果和所得结论进行概括。
  摘要应具有独立性和自明性，其内容应包含与论文全文同等量的主要信息。
  使读者即使不阅读全文，通过摘要就能了解论文的总体内容和主要成果。
  摘要包括研究目的、方法、结果和结论，要突出论文的创造性成果。摘要中不可出现参考文献、图、表、化学结构式、非公知公用的符号和术语。
  
  论文摘要的书写应力求精确、简明。
  切忌写成对论文书写内容进行提要的形式，尤其要避免“第 1 章……；第 2 章……；……”这种或类似的陈述方式。
  
  英文摘要与中文摘要内容应一致。硕士学位论文摘要不少于 500 字，博士学位论文摘要不少于 1000 字。
  
  关键词是为了便于文献索引和检索，从论文中选取出来用以表示全文主题内容信息的术语。
  关键词一般选 5\textasciitilde8 个专业术语，中、英文关键词须对应。

  % 关键词用“英文逗号”分隔，输出时会自动处理为正确的分隔符
  \thusetup{
    keywords = {关键词 1, 关键词 2, 关键词 3, 关键词 4, 关键词 5},
  }
\end{abstract}

\cleardoublepage
\begin{abstract*}
  An abstract of a dissertation is a summary and extraction of research work and contributions.
  Included in an abstract should be description of research topic and research objective, brief introduction to methodology and research process, and summarization of conclusion and contributions of the research.
  An abstract should be characterized by independence and clarity and carry identical information with the dissertation.
  It should be such that the general idea and major contributions of the dissertation are conveyed without reading the dissertation.

  An abstract should be concise and to the point.
  It is a misunderstanding to make an abstract an outline of the dissertation and words “the first chapter”, “the second chapter” and the like should be avoided in the abstract.

  Keywords are terms used in a dissertation for indexing, reflecting core information of the dissertation.
  An abstract may contain a maximum of 5 keywords, with semi-colons used in between to separate one another.

  % Use comma as seperator when inputting
  \thusetup{
    keywords* = {keyword 1, keyword 2, keyword 3, keyword 4, keyword 5},
  }
\end{abstract*}
